Artin Group Presentations Arising from Cluster Algebras

### 2014-07-20 Paper.tex
fixed title

\title{Artin Group Presentations of Reflection Groups}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{you can put addresses for authors\\
here \\
Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
\email{aaronlandesman@college.harvard.com, jhaley3@nd.edu, david.hemminger@duke.edu, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}

>>>>

\title{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
\address{you can put addresses for authors\\
here \\
Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
\date{\today}
\keywords{Artin group, cluster algebra, diagram representations}
